\appendix

\chapter{Ethics Checklist}
\autoref{tab:ethicschecklist} presents an abridged version of the \emph{Ethics Checklist} provided by the Department of Computing. Issued identified in the checklist are discussed in length in \autoref{sec:ethics}.

\begin{longtable}{p{0.01\textwidth}>{\raggedright}p{0.85\textwidth}r}
\toprule
   \multicolumn{2}{l}{Section 1: Humans} \\
   & Does your project involve human participants? & \cmark \\
\midrule
   \multicolumn{2}{l}{Section 2: Protection of Personal Data} \\
   & Does your project involve personal data collection and/or processing? & \cmark \\
   & Does it involve the collection and/or processing of sensitive personal data? & \cmark \\
   & Does it involve processing of genetic information? & \xmark \\
   & Does it involve tracking or observation of participants? & \xmark \\
   & Does your project involve further processing of previously collected personal data (secondary use)? & \cmark \\
   \multicolumn{2}{l}{Section 3: Animals} \\
   & Does your project involve animals? & \xmark \\
   \multicolumn{2}{l}{Section 4: Developing Countries} \\
   & Does your project involve developing countries? & \cmark \\
   & If your project involves low and/or lower-middle income countries, are any benefit-sharing actions planned? & \xmark \\
   & Could the situation in the country put the individuals taking part in the project at risk? & \xmark \\
\midrule 
   \multicolumn{2}{l}{Section 5: Environmental Protection and Safety} \\
   & Does your project involve the use of elements that may cause harm to the environment, animals or plants? & \xmark \\
   & Does your project involve the use of elements that may cause harm to humans, including project staff? & \xmark \\
\midrule 
   \multicolumn{2}{l}{Section 6: Dual Use} \\
   & Does your project have the potential for military applications? & \xmark \\
   & Does your project have an exclusive civilian application focus? & \cmark \\
   & Will your project use or produce goods or information that will require export licenses in accordance with legislation on dual use items? & \xmark \\
   & Does your project affect current standards in military ethics? & \xmark \\
\midrule 
   \multicolumn{2}{l}{Section 7: Misuse} \\
   & Does your project have the potential for malevolent/criminal/terrorist abuse? & \xmark \\
   & Does your project involve information on/or the use of biological-, chemical-, nuclear/radiological-security sensitive materials and explosives, and means of their delivery? & \xmark \\
   & Does your project involve the development of technologies or the creation of information that could have severe negative impacts on human rights standards, if misapplied? & \xmark \\
   & Does your project have the potential for terrorist or criminal abuse? & \xmark \\
\midrule 
   \multicolumn{2}{l}{Section 8: Legal Issues} \\
   & Will your project use or produce software for which there are copyright licensing implications? & \cmark \\
   & Will your project use or produce goods or information for which there are data protection, or other legal implications? & \cmark \\
\midrule 
   \multicolumn{2}{l}{Section 9: Other Ethics} \\
   & Are there any other ethics issues that should be taken into consideration? & \xmark \\
\bottomrule \\

\caption{Ethics Checklist}
\label{tab:ethicschecklist}
\end{longtable}

